Redundant calibration as a complex optimization problem

### 2017-01-09 paper.tex
added prec error results

\subsection{Redundant Measurement Equation}
\label{sec:r_mes}
If the array is redundant and the function $\phi_{pq}$ is known we can rewrite Eq.~\eqref{eq:vis_definition} as
\begin{equation}
\label{eq:vis_red}
d_{pq} = g_{p}\conj{g_q}y_{\phi_{pq}} + n_{pq}.
\end{equation}
Eq.~\eqref{eq:vis_red} can also be expressed in the following vector form 
\begin{equation}
\label{eq:vis_red_vec}
\bd = \bv + \bn, 
\end{equation}
where 
\begin{align}
 \left [ \bd \right]_{\alpha_{pq}} &= d_{pq}, & \left [ \bv \right ]_{\alpha_{pq}} &= g_p y_{\phi_{pq}} \conj{g_q},\nonumber\\
 \left [ \bn \right ]_{\alpha_{pq}} &= n_{pq}. &  &\label{eq:vec_definitions}
\end{align}
The vectors in Eq.~\eqref{eq:vec_definitions} are column vectors of size $B$ (i.e. $p<q$).

@@

Eq.~\eqref{eq:g_update} and Eq.~\eqref{eq:y_update} are the exact same iterative new parameter estimators derived by \citet{Marthi2014}. Als note that Eq.~\eqref{eq:g_update} is the fundamental
gain estimator associated with StEfCal. We have therefore successfully used the diagonal approximation approach suggested by \citet{Smirnov2015} to re-derive the ADI method presented in 
\citet{Marthi2014} and in doing so we have shown that the algorithm in \citet{Marthi2014} is actually redundant StEfCal. We could also have shown this by using a similar approach 
to the one presented in \citet{Salvini2014}.

The question now arises what value should we use for $\alpha$? In \citet{Marthi2014} they propose 
$\alpha = 0.3$. Although an exact mathematical proof for the optimal choice of $\alpha$ still eludes us, it is still possible to
venture a clever guess by studying what the choice of $\alpha$ is in the case of skymodel-based StEFCal. Recall from Section~\ref{sec:sbc} that $\alpha$ is equal to a half 
in the case of StEFCal (for even iterations). If we wish to mimic this behaviour for the redundant calibration use case we need to scale $\breve{\bz}$ by two thirds in Eq.~\eqref{eq:alpha} (see Eq.~\eqref{eq:two_thrids}) which implies that we should choose $\alpha$ equal to a third, which corresponds to a $\lambda$ equal to two.
We used $\lambda$ equal to two in this paper.

\begin{figure}
\includegraphics[width=0.47\textwidth]{./prec_error.pdf} 
\caption{Precentage Error}
\label{fig:prec_error}
\end{figure}

>>>>

\subsection{Redundant Measurement Equation}
\label{sec:r_mes}
If the array is redundant and the function $\phi_{pq}$ is known we can rewrite Eq.~\eqref{eq:vis_definition} as
\begin{equation}
\label{eq:vis_red}
d_{pq} = g_{p}\conj{g_q}y_{\phi_{pq}} + n_{pq}.
\end{equation}
Eq.~\eqref{eq:vis_red} can also be expressed in the following vector form 
\begin{equation}
\label{eq:vis_red_vec}
\bd = \bv + \bn, 
\end{equation}
where 
\begin{align}
 \left [ \bd \right]_{\alpha_{pq}} &= d_{pq}, & \left [ \bv \right ]_{\alpha_{pq}} &= v_{pq}=g_p y_{\phi_{pq}} \conj{g_q},\nonumber\\
 \left [ \bn \right ]_{\alpha_{pq}} &= n_{pq}. &  &\label{eq:vec_definitions}
\end{align}
The vectors in Eq.~\eqref{eq:vec_definitions} are column vectors of size $B$ (i.e. $p<q$).

@@

Eq.~\eqref{eq:g_update} and Eq.~\eqref{eq:y_update} are the exact same iterative new parameter estimators derived by \citet{Marthi2014}. Als note that Eq.~\eqref{eq:g_update} is the fundamental
gain estimator associated with \textsc{StEfCal}. We have therefore successfully used the diagonal approximation approach proposed by \citet{Smirnov2015} to re-derive the ADI method presented in 
\citet{Marthi2014} and in doing so we have shown that the algorithm in \citet{Marthi2014} is actually redundant StEfCal. We could also have shown this by using a similar approach 
to the one presented in \citet{Salvini2014}.

The question now arises what value should we use for $\alpha$? In \citet{Marthi2014}, they propose 
$\alpha = 0.3$. Although an exact mathematical proof for the optimal choice of $\alpha$ still eludes us, it is still possible to
venture a clever guess by studying what the choice of $\alpha$ is in the case of skymodel-based \textsc{StEFCal}. The value of $\alpha$ is equal to a half 
in the case of \textsc{StEFCal} (for even iterations); see Appendix~\ref{sec:sbc}. If we wish to mimic this behaviour for the redundant calibration use case we need to scale $\breve{\bz}$ by two thirds in Eq.~\eqref{eq:alpha} (see Eq.~\eqref{eq:two_thrids}) which implies that we should choose $\alpha$ equal to a third, which corresponds to a $\lambda$ equal to two.
We used $\lambda$ equal to two in this paper.

Optimality results of ADI were presented in \citet{Marthi2014}. We do not repeat their analysis here. We however, do present our own ADI results in Fig.~\ref{fig:prec_error} that confirm that the
ADI method can accurately estimate the antenna gains and the observed visibilities at different SNR values. To quantity the exact error in our estimates we used the precentage error $\beta$ defined 
as 
\begin{equation}
\label{eq:beta}
\beta = \frac{\sum_{pq} |v_{pq} - \widehat{v}_{pq} |^2}{v_{pq}}.
\end{equation}
We have already defined $v_{pq}$ in Eq.~\eqref{eq:vec_definitions}. Moreover, in Eq.~\eqref{eq:beta}, $\widehat{v}_{pq}$ denotes the ADI estimate of $v_pq$.

\begin{figure}
\includegraphics[width=0.47\textwidth]{./prec_error.pdf} 
\caption{We plot the precentage error $\beta$ between the estimated 
predicted visibilities and the true predicted visibilities for different SNR values as a function of the number of antennas in the array $N$. The graph presented here was generated using the first experimental setup in Table~\ref{tab:ch_parm}.}
\label{fig:prec_error}
\end{figure}
